Local Tuning in Peano Curves-based Global Optimization Scheme

### 2016-09-19 2016/YSC/ysc_paper.tex
Update conclusion in YSC paper

\begin{figure}[ht]
    \centering
    \subfloat[global \(H\) estimation]{{\includegraphics[width=0.45\textwidth]{images/gkls_glob.png} }}
    \qquad
    \subfloat[local-adaptive \(H\) estimation]{{\includegraphics[width=0.45\textwidth]{images/gkls_loc.png} }}
    \caption{The contour plots of a function from GKLS class}
    \label{fig:gkls_isolines}
\end{figure}
\par
Next, let us go to the comparison of various variants of the method for the problem
classes considered. In order to evaluate the efficiency of an algorithm, we will use
the operating characteristics \cite{grishaginClass}, which is defined by a set of points on the \((K, P)\)
plane where \(K\) is the averaged number of the search trials carried out before the satisfaction
of the termination condition when minimizing a function from given class, and \(P\)
is portion of problems solved successfully. If at given \(K\) the operating characteristic
of a method goes higher than the one of another method, it means that at fixed costs
of the search the former method will find the solution with a greater probability.
If some value of \(P\) is fixed, and the characteristic of a method goes to the left from
the one of another method, the former method requires fewer resources to achieve the same reliability.
\par
\begin{figure}[ht]
  	\center
    \includegraphics[width=0.75\textwidth]{images/grishagin.png}
    \caption{Operating characteristics of the methods compared on \(F_{GR}\) problems class}
    \label{fig:grishh_op}
  \end{figure}
As it is seen from the operating characteristics in Fig. \ref{fig:grishh_op}, \ref{fig:gkls_op}, both methods with the
local adaptive estimate of Hölder constant have demonstrated an essential advantage.
However, both methods require setting a higher value of the parameter \(r\). If one compares the
methods with the adaptive convolution and  with the non-adaptive one (\ref{additiveConv})(\ref{additiveAdaptiveConv}), the advantage
of the latter is seen clearly, although it requires a higher value of the reliability
parameter \(r\) to solve the problems form GKLS class.
  \begin{figure}[ht]
  	\center
    \includegraphics[width=0.75\textwidth]{images/gkls-s.png}
    \caption{Operating characteristics of the methods compared on GKLS problems class}
    \label{fig:gkls_op}
  \end{figure}
%------------------------------------------------------------------------------
\section{Conclusions}
In the present paper, the application of the methods of accounting for the local
properties of the objective function
in the multidimensional multiextremal optimization problems has been considered. Taking
into account the local properties is expressed in the use of different estimates of Hölder
constant in different search domains. The efficiency of the considered approach has been
confirmed by solving the series of multidimensional problems form two classes.

>>>>

\begin{figure}[ht]
    \centering
    \subfloat[global \(H\) estimation]{{\includegraphics[width=0.45\textwidth]{images/gkls_glob.png} }}
    \qquad
    \subfloat[local-adaptive \(H\) estimation]{{\includegraphics[width=0.45\textwidth]{images/gkls_loc.png} }}
    \caption{The contour plots of a function from GKLS class}
    \label{fig:gkls_isolines}
\end{figure}
\par
Next, let us go to the comparison of various variants of the method for the problem
classes considered. In order to evaluate the efficiency of an algorithm, we will use
the operating characteristics \cite{grishaginClass}, which is defined by a set of points on the \((K, P)\)
plane where \(K\) is the averaged number of the search trials carried out before the satisfaction
of the termination condition when minimizing a function from given class, and \(P\)
is portion of problems solved successfully. If at given \(K\) the operating characteristic
of a method goes higher than the one of another method, it means that at fixed costs
of the search the former method will find the solution with a greater probability.
If some value of \(P\) is fixed, and the characteristic of a method goes to the left from
the one of another method, the former method requires fewer resources to achieve the same reliability.
\par
\begin{figure}[ht]
  	\center
    \includegraphics[width=0.75\textwidth]{images/grishagin.png}
    \caption{Operating characteristics of the methods compared on \(F_{GR}\) problems class}
    \label{fig:grishh_op}
  \end{figure}
As it is seen from the operating characteristics in Fig. \ref{fig:grishh_op}, \ref{fig:gkls_op}, both methods with the
local adaptive estimate of Hölder constant have demonstrated an essential advantage.
However, both methods require setting a higher value of the parameter \(r\). If one compares the
methods with the adaptive convolution and  with the non-adaptive one (\ref{additiveConv})(\ref{additiveAdaptiveConv}), the advantage
of the latter is seen clearly, although it requires a higher value of the reliability
parameter \(r\) to solve the problems form GKLS class.
  \begin{figure}[ht]
  	\center
    \includegraphics[width=0.75\textwidth]{images/gkls-s.png}
    \caption{Operating characteristics of the methods compared on GKLS problems class}
    \label{fig:gkls_op}
  \end{figure}
%------------------------------------------------------------------------------
\section{Conclusions}
In the present work, the global optimization problems and the deterministic methods
for solving these ones are considered. The relevance of solving the problems of this
class is defined by the importance of the applications (optimal design, problems of
parameter identification, pattern recognition, signa processing, etc.). The multiextremal
(global) optimization methods are extremely computation costly since these ones require
the constructing and using of the adaptive models of the objective function behavior
according to the trial results accumulated during the algorithm execution.
\par
In this work, the application of the method of accounting for the local behavior of
the optimized function within the multidimensional multiextremal optimization method
has been considered. Earlier, this method has been applied to the one-dimensional
problems only. Taking into account the local properties is implemented in the use of
different estimates of Hölder constant in different search domains. Thus, the process
of solving the problem is accelerated significantly by means of reducing the number of
the search trials.
\par
The comparison of two different schemes of constructing the estimates of Hölder constant
(\ref{additiveConv}), (\ref{additiveAdaptiveConv}) has revealed the advantage of scheme (\ref{additiveConv}).
However, a larger value of the reliability parameter of the search method \(r\) might be required
to use this scheme for solving some problems. When solving the complex problems with a small
area of attraction of the global extremum, scheme (\ref{additiveAdaptiveConv}) is preferable for
more reliability of the method. The efficiency of the considered approach has been confirmed
by solving the series of multidimensional problems form two classes.
